My title

### 2024-02-19 paper/paper.qmd
Committing all changes up to date on paper.qmd (Feb 18 @ 10:16pm

library(stats)
library(knitr)
library(kableExtra)
library(broom)
library(dplyr)
library(ggplot2)
library(tidyverse)

@@

# Introduction

The intersection of race and criminal justice policy in the United States has long been a point of contention, marked by notable divergences in perception between Black and White Americans. Predominant assumptions suggest a steady punitive stance in U.S. public opinion towards criminal justice issues, with such punitiveness among Whites often attributed to underlying anti-Black prejudice @BoboJohnson2004. This phenomenon is particularly pronounced in the context of the war on drugs, where drug epidemics are often portrayed negatively within society, with a tendency to associate such crises predominantly with non-White and minority communities. This portrayal not only reinforces stigmatizing stereotypes but also influences public opinion and policy.

In recent years the United States has experienced a shift in racial framing and valence within media and society. Despite similar rates of illicit drug use among Black and White Americans throughout history, Black Americans are significantly more likely to be incarcerated for drug offenses. In contrast, White Americans, especially in the context of the opioid crisis, experience a more lenient, medicalized approach to their drug use, revealing a racialized American drug policy @NetherlandHansen2017.

@@

The study revealed that when opioid users, both White and Black, were shown in a sympathetic light, White people's support for treatment options rose. However, this supportive attitude was noticeably stronger when the users depicted were White, pointing to a bias in empathy based on race. Essentially, White Americans showed a preference for offering treatment to individuals of their own racial background. On the other hand, portrayals lacking sympathy didn't really change opinions, regardless of the user's race @Raychaudhuri2022.

This paper aims to replicate the study conducted by Raychaudhuri, Mendelberg, and McDonough, focusing on their original research question: "Is sympathy for drug users racially selective among White Americans?" However, it will extend the inquiry by examining the role of political ideology in shaping White Americans' reactions to sympathetic media portrayals of opioid abuse. Specifically, it will investigate whether political ideology conditions the extent of racial selectivity in empathetic responses to drug users. The paper will reveal that there is some level of there is indeed some interaction effect between media frames and the ideological spectrum on support for treatment related policy.

@@

```{r}
#| warning: false
#| echo: false
#| label: tbl-cleaned_data
#| tbl-cap: Cleaned Data

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

head(analysis_data)

@@

```{r}
#| warning: false
#| echo: false
#| label: tbl-terms_explanation_table
#| tbl-cap: Explanation of Terms in the Coefficient Table

@@

```{r}
#| warning: false
#| echo: false
#| label: fig-policy_vs_media_frames
#| fig-cap: Policy Support by Valence and Race (Media Frames)

@@

```{r}
#| warning: false
#| echo: false
#| label: fig-interactions
#| fig-cap: Interaction effects of political ideology and media framing on policy support

>>>>

library(stats)
library(knitr)
library(kableExtra)
library(broom)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(kableExtra)

@@

# Introduction
In recent years the United States has experienced a shift in racial framing and valence within media and society. Despite similar rates of illicit drug use among Black and White Americans throughout history, Black Americans are significantly more likely to be incarcerated for drug offenses. This phenomenon is particularly pronounced in the context of the war on drugs @BoboJohnson2004. In contrast, White Americans, especially in the context of the opioid crisis, experience a more lenient, medicalized approach to their drug use, revealing a racialized American drug policy @NetherlandHansen2017.

@@

The study revealed that when opioid users, both White and Black, were shown in a sympathetic light, White people's support for treatment options rose. This supportive attitude was noticeably stronger when the users depicted were White, pointing to a bias in empathy based on race. On the other hand, portrayals lacking sympathy didn't really change opinions, regardless of the user's race @Raychaudhuri2022.

This paper aims to replicate the study conducted by Raychaudhuri, Mendelberg, and McDonough, focusing on their original research question: "Is sympathy for drug users racially selective among White Americans?" However, it will extend the inquiry by examining the role of political ideology in shaping White Americans' reactions to sympathetic media portrayals of opioid abuse. Specifically, it will investigate whether political ideology conditions the extent of racial selectivity in empathetic responses to drug users. The paper will reveal that there is some indeed some level of interaction effect between media frames and the ideological spectrum on support for treatment related policy.

@@

```{r}
#| warning: false
#| echo: false
#| fig.pos: 'H'
#| label: tbl-cleaned_data
#| tbl-cap: Cleaned Data

# Read the dataset
analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

# Output a nicely formatted table of the first five rows of the dataset
kable(head(analysis_data, 5), "latex", booktabs = TRUE) |>
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 5)

@@

```{r}
#| warning: false
#| echo: false
#| fig.pos: 'H'
#| label: tbl-terms_explanation_table
#| tbl-cap: Explanation of Terms in the Coefficient Table

@@

```{r}
#| warning: false
#| echo: false
#| fig.pos: 'H'
#| label: fig-policy_vs_media_frames
#| fig-cap: Policy Support by Valence and Race (Media Frames)

@@

```{r}
#| warning: false
#| echo: false
#| label: fig-interactions
#| fig.pos: 'H'
#| fig-cap: Interaction effects of political ideology and media framing on policy support
